\ProvidesFile{ap-bugs}[2021-08-23 bugs appendix]

\newcommand{\bug}{\vspace{6pt}}  
\newcommand{\checkedok}[1]{{\bfseries Checked ok on #1.}}
\newcommand{\waitingon}[1]{{\bfseries Waiting on #1.}}

\chapter{BUGS}

See ap-bugs.tex file for \LaTeX\ input.


\section{These problems need to be fixed}

% I need to fix the following things in \PurdueThesis.
% They are listed in decreasing order in priority.

\bug
Allow manual line break in \verb+\title+.
{\small (Mark Senn <mark@purdue.edu>.)}

\bug
Allow comma in \verb+\title+.
{\small (Mark Senn <mark@purdue.edu>).}

\bug
Table of Contents uses double-spaced instead of 1\sfrac12 spacing.
Tighten up section and less significant heading spacing?
{\small (Anita Adams Sale <aasale@iupui.edu>, 2021-03-17, 11:16.)}
 
\bug
List of Figures indented $\approx$\sfrac14 inch
more than List of Tables.
{\small (Anita Adams Sale <aasale@iupui.edu>, 2021-03-17, 11:16.)}

\bug
Left reference section margin is ok if a person has 10--99 references.
Figure out how to adjusting margin for 1--9 or over 99 references.
{\small (Mark Senn <mark@purdue.edu>.)}

\bug
Change citation, e.g., ``[6], [71]'' to ``[6,71]''.
{\small (Mark Senn <mark@purdue.edu>, 2021-04-07, 11:55.)}

\bug
Change citation, e.g., ``[6], [7], [8]'' to ``[6-8]''.
{\small (Mark Senn <mark@purdue.edu>, 2021-04-07, 11:55.)}

\bug
APA reference style indents references too far on left.
{\small (Mark Senn <mark@purdue.edu>, 2021-04-08, 21:42.)}

\bug
Use ``Last Accessed: dd/mm/yy.'' urldate in bibliography.
{\small (Priyank Kalgaonkar <pkalgaon@iupui.edu>, 2021-04-06, 15:58.)}

\bug
Use ``Last Accessed: yyyy-mm-dd.'' urldate in bibliography.
{\small (Mark Senn <mark@purdue.edu>, 2021-04-19, 17:05.)}

\bug
Check that \verb+@{}+ is before the left column
and after the right column in all tables.
{\small (Mark Senn <mark@purdue.edu>, 2021-04-19, 21:32.)}

\bug  
Add DTECH degree.


\section{These issues have been reported}

\bug
Bibliography change.
Change,
for example,
``Acoustical Science and Technology, vol.~23, no.~1''
to
``Acoustical Science and Technology {\bfseries 23\/} ({\bfseries 1\/})''.
{\small (Daniel Joesph Carr <djcarr@purdue.edu>, 2021-06-16, 09:33.)}

\bug
Bibliography change.
Change,
for example,
``M.~Abramowitz and I.A.~Stegun, Eds.,''
to
``M.~Abramowitz and I.A.~Stegun, editors,''
{\small (Daniel Joesph Carr <djcarr@purdue.edu>, 2021-06-16, 09:33.)}

\bug
Section headings containing a SmallCaps font do not work.
{\small (Javad (Nima) Darivandpour" <jdarivan@purdue.edu>, 2021-06-29, 10:25.}
See \ref{section-headings-with-smallcaps-font}

\section{These problems are waiting on a reply}

\verb+linktoc = section+ does not work with captions with \verb+\frac+.
{\small
  (Mark Senn <mark@purdue.edu>, 2021-05-27, 13:09.
  In the short-term check with Ashlee Messersmith <amiley@purdue.edu>
  if \verb+linktoc = page+ can be used.
  If that's ok make the change
  and look into changing captions from my code
  to \LaTeX's code.)%
}
\waitingon{Ashlee}


\section{These problems have been fixed}

Non-nested description environments have bold items.
Nested description environments have non-bold items.
How come?
Are the indentations correct?
{\small (Mark Senn <mark@purdue.edu>, 2021-04-09, 16:49.)}
\checkedok{2021-05-31}

