\ProvidesFile{ch-front.tex}[2021-08-23 front matter chapter]
%
%  This is ``front matter'' for the thesis.
%
%  REFERENCES
%
%    TCMOS17
%      The Chicago Manual of Style Online, 17th edition.
%      https://www.chicagomanualofstyle.org/home.html
%      retrieved on 2020-02-29
%
%    TEMPL
%      Thesis and Disertation Office Templates.
%      https://www.purdue.edu/gradschool/research/thesis/templates.html
%      retrieved on 2020-02-29
%
%    WNNCD
%    Webster's Ninth New Collegiate Dictionary.
%

%
%   Only Purdue University uses this page
%
%   Comment out \begin{statement} through \end{statement}
%   if you are not at Purdue University.
%
% Statement of Thesis/Dissertation Approval Page
% This page is REQUIRED.  The page should be numbered "2"
% and should NOT be listed in your TABLE OF CONTENTS.
\begin{statement}
  % Delete or add \entry commands as needed for all committe members.
  \entry{Dr.~Gaurav Chopra, Chair}{Department of Chemistry}
  \entry{Dr.~Hilkka I. Kentämaa}{Department of Chemistry}
  \entry{Dr.~Herman O. Sintim}{Department of Chemistry}
  \entry{Dr.~David Thompson}{Department of Chemistry}
  % There should be one \approvedby command containing the
  % "FORM 9 THESIS FORM HEAD NAME HERE" (from TEMPL, retrieved on 2020-03-01).
  \approvedby{Dr.~Christine A. Hrycyna}
     Head of the School Graduate Program\\
\end{statement}

% Dedication page is optional.
% A name and often a message in tribute to a person or cause.
% References: WEB9 332.
\begin{dedication}
  This thesis is dedicated to the mentors and advisors who have supported me
  throughout my education.
\end{dedication}

% Acknowledgements page is optional but most theses include
% a brief statement of appreciation or recognition of special
% assistance.
\begin{acknowledgments}
  I would like to acknowledge the various individuals, whom without their support and insight, this thesis would not exists.  
  Firstly, I would like to thank my advisor, Dr. Gaurav Chopra, for his infinite patience and support.  Additionally, beyond his endless emotional support as a friend, the mentorship of Jonathan Fine was critical for the development of both my coding abilities and critical thinking as a scientist.  I would also like to thank Krupal Jethava for assisting with organic synthesis, and his insight regarding transformations involved in the development of a solvent prediction machine learning pipeline. For the work regarding an autonomous HPLC-MS, I would like to thank Ruth Anyaeche and Prageeth Rajitha in addition to Dr. Hilkka Kentämaa. 
\end{acknowledgments}

% The preface is optional.
% References: TCMOS17 1.49, WEB9 927.
\begin{preface}
  This is the preface.
\end{preface}

% The Table of Contents is required.
% The Table of Contents will be automatically created for you
% using information you supply in
%     \chapter
%     \section
%     \subsection
%     \subsubsection
%     commands.
\pdfbookmark{TABLE OF CONTENTS}{Contents}
\tableofcontents

% If your thesis has tables, a list of tables is required.
% The List of Tables will be automatically created for you using
% information you supply in
%     \begin{table} ... \end{table}
% environments.
\listoftables

% If your thesis has figures, a list of figures is required.
% The List of Figures will be automatically created for you using
% information you supply in
%     \begin{figure} ... \end{figure}
% environments.
\listoffigures

% If your thesis has protocols, you may want to do a list of protocols.
% The List of Protocols will be automatically created for you using
% information you supply in
%     \begin{protocol} ... \end{protocol}
% environments.
\listofprotocols

% If your thesis has schemes, you may want to do a list of schemes.
% The List of Schemes will be automatically created for you using
% information you supply in
%     \begin{scheme} ... \end{scheme}
% environments.
\listofschemes

% List of Symbols is optional.
\begin{symbols}
  $m$& mass\cr
  $v$& velocity\cr
\end{symbols}

% List of Abbreviations is optional.
\begin{abbreviations}
  DP& Diagnostic Product\cr
  DT& Decision Tree\cr
  GMM& Gaussian Mixture Models\cr
  GUI& Graphical User Interface\cr
  JT-VAE& Junction Tree Variational Autoencoder\cr
  ML& Machine Learning\cr
  MLP& Multi-Layer Perceptron Neural Network\cr
  PT& Proton Transfer\cr
  RMSD& Root Mean Squared Deviation\cr
  ROC& Receiver Operator Characteristic\cr
\end{abbreviations}

% Nomenclature is optional.
\begin{nomenclature}
  MOP& 2-methoxy propylene\\
  TDMAB& tris(dimethylamino)borane\\
  TMB& trimethyl borate\\

\end{nomenclature}

% Glossary is optional.
\begin{glossary}
  philtrum& the groove between the nose and upper lip\\
  septem& the cartilage in the nose that separates the nostrils\\
  supercalifragilisticexpialidocious&
    a nonsense word,
    originally used esp.~by children,
    and typically expressing excited approbation:
    fantastic,
    fabulousextraordinarily good \cite{super...}\\
  test entry&
    This is a a long test sentence.\\
\end{glossary}

% Abstract is required.
% Note that the information for the first paragraph of the output
% doesn't need to be input here...it is put in automatically from
% information you supplied earlier using \title, \author, \degree,
% and \majorprof.
% Reference: PU 17.
\begin{abstract}
\noindent
Beck, Armen G. Ph.D., Purdue University, December 2022.  Bit by Bit Chemistry: Data Driven Software for Chemical Systems.  Major Professor: Gaurav Chopra\\

  \PurdueThesisLogo\ is a \LaTeX\ document class used for
  master's bypass reports,
  master's theses,
  PhD dissertations,
  and PhD preliminary reports.
  This template demonstrates how to use \PurdueThesisLogo.

\end{abstract}
